We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-24 paper/paper.tex
new data in table

However, the tipicallity of satellite distributions can be addressed
in simulations.
Most of the studies have been performed in the currently preferred
paradigm, which is based on a Cold Dark Matter cosmology in a expanding
Universe described by General Relativity including a Cosmological
Constant, the so-called Lambda Cold Dark Matter (LCDM).
The broad consensus is that these highly structured satellite distributions
are hard to find in simulations.  
There are still disagreements on the precise degree of atypicallity
and the conditions required to simulate

@@

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-9}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
  \end{tabular}
  \caption{Mean values and standard deviations for the different
    quantities describing satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. The first colum refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data. 
    The third column summarizes the results from the 20 pairs in
    Illustris-1 and the last column corresponds to the 12 pairs in the
    ELVIS project.}
\end{table*}

>>>>

However, the tipicallity of satellite distributions can be addressed
in simulations.
Most of the studies have been performed in the currently preferred
paradigm, which is based on a Cold Dark Matter cosmology in a expanding
Universe described by General Relativity including a Cosmological
Constant, the so-called Lambda Cold Dark Matter (LCDM).
The broad consensus is that these highly structured satellite distributions
are hard to find in simulations.  
There are still disagreements on the precise degree of atypicallity
and the conditions required to simulate satellite distributions closer

@@

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
  \end{tabular}
  \caption{Mean values and standard deviations for the different
    quantities describing satellite distribution: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first colum refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data. 
    The third column summarizes the results from the 20 pairs in
    Illustris-1 and the last column corresponds to the 12 pairs in the
    ELVIS project.}
\end{table*}

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Illustris-1-DM}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $62\pm 3$   & $61\pm 3$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
    $c/a$ ratio & $0.50\pm0.01$ & $0.50\pm 0.02$ & $0.52\pm 0.01$ & $0.53\pm 0.01$ & $0.54\pm 0.01$& $0.49\pm 0.02$ \\ \hline
    $b/a$ ratio & $0.79\pm0.01$ & $0.81\pm 0.02$ & $0.80\pm 0.01$ & $0.80\pm 0.02$ & $0.80\pm0.01$& $0.81\pm 0.01$\\ \hline
  \end{tabular}
  \caption{Mean values and standard deviations for the different
    quantities describing satellite distributions: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first column summarize the results from the 24 pairs in
    Illustris-1-DM, the second column from the 20 pairs in
    Illustris-1 and the third column from the 12 pairs in the
    ELVIS project.}
\end{table*}
